\documentclass[letterpaper]{article}

\usepackage{yojibook}
\usepackage{multicol}

\hypersetup {
 pdfauthor= Rose DiFonzo,
 pdftitle={Four Character Yojijukugo, よじじゅくご,   },
 pdfsubject={kanji },
 pdfkeywords={kanji, japan, wanikani, vocabulary,Four Character Yojijukugo },
 }
 

\begin{document}

\fontsize{24}{24}
\vfill

\begin{center}
\begin{multicols}{2}
\RLmulticolcolumns
六十万歳\\
鰐蟹四字\\
\end{multicols}
\vfill
\hspace{0pt}

RoseWagsBlue\\
\the\year\ \\
Coneko Press
\end{center}



%\newpage
%*
%\newpage
%\fontsize{9}{9}
%\noindent
%四字熟語, よじじゅくご, are four character idiomatic compounds.  They are often littlle folk expressions, condensed into four characters, like a form of poetry.  Many of them originated in China.  The 四字熟語 in this book are about Wanikani, written by Wanikani members.  
%\pagenumbering{gobble}
\newpage

\definitionpage{鰐頭蟹胴}{がくとうかいどう}{Head of an alligator,\\ body of a crab}{Leebo}{'gator head crab body}
\definitionpage{迅敗徐勝}{じんぱいじょしょう}{Failing going fast, winning going slowly (motto for team slow)}{Leebo}{swift failure slow win}
\definitionpage{昼夜熱勉}{ちゅうやねつべん}{Passionate studying day and night (motto for team fast)}{Leebo}{day night passion exertion}
\definitionpage{燃々亀々}{ねんねんきき}{Burn burn turtle turtle}{Leebo}{}
\definitionpage{音訓混同}{おんくんこんどう}{Mixing up onyomi and kunyomi}{Leebo}{sound reading mix same}
\definitionpage{快苦死獄}{かいくしごく}{The first forty levels of WaniKani}{Leebo}{pleasant painful death hell}
\definitionpage{天国現実}{てんごくげんじつ}{The last twenty levels of WaniKani}{Leebo}{heavens country exist truth\\(paradise reality)}
\definitionpage{見答辞典}{みどうじてん}{Looking up answers on dictionary, cheating.}{VictorLino}{see solution word code}
\definitionpage{変読成泣}{へんどくせっきゅう}{Jukugo that have\\ unexpected readings.}{VictorLino}{strange readings\\ make cry}
\definitionpage{千新教訓}{せんしんきょうくん}{Being overwhelmed with new lessons (usually after level up).}{VictorLino}{thousand new\\ teach instruction}
\definitionpage{遅始要釈}{ちしようしゃく}{Demanding an explanation for the slow start}{Leebo}{slow begin\\ need explanation}
\definitionpage{不用用可}{ふようようか}{Not useful, but could be useful}{Leebo}{not use use can}
\definitionpage{中止赤点}{ちゅうしあかてん}{Failing a test after taking a hiatus}{milkyrose}{middle stop red spot}
\definitionpage{過迅失敗}{かじんしっぱい}{Speed-related typos}{LucasDesu}{exceed swift lose failure}
\definitionpage{多問再始}{たもんさいし}{Overwhelmed by reviews, reset}{LucasDesu}{many question again\\ begin}
\definitionpage{進図自慢}{しんずじまん}{Bragging about progress with a graph}{LucasDesu}{advance map oneself\\ ridicule}
\definitionpage{無探投稿}{むたんとうこう}{Creating a new topic\\ without searching first}{LucasDesu}{no search throw draft}
\definitionpage{並直乱用}{へいちょくらんよう}{Re-order script abuse}{Houndstooth}{row fix riot use}
\definitionpage{読書混同}{よみかきこんどう}{Mixing up reading and meaning when answering the quiz.}{jneapan}{read write confuse same}
\definitionpage{例外馴染}{れいがいなじみ}{Getting used to exceptions.}{jneapan}{example outside tamed color}
\definitionpage{読二答一}{どくにとういつ}{Read twice, answer once.}{Kazzeon}{}
\definitionpage{古宇偉知}{こういち}{Fill your empty head with great knowledge}{Belthazar}{old roof admirable know}
%% \definitionpage{復習一過}{ふくしゅういっか}{The calm following a\\ review storm.  }{Kqaotix}{restore learn one exceed}
\definitionpage{復習暗殺}{ふくしゅうあんさつ}{When that huge review batch comes in from\\ clearing a review backlog ages ago}{Houndstooth}{restore learn darkness kill}
\definitionpage{復習回避}{ふくしゅうかいひ}{Evasion of reviews (by going to the forums)}{TamanegiNoKame}{restore learn revolve evade}
\definitionpage{全遊無働}{ぜんゆうむどう}{All play and no work}{TamanegiNoKame}{}
\definitionpage{多喋少習}{たちょうしょうしゅう}{Much chatter,\\ little learning}{Saruko}{}
\definitionpage{漢字和語}{かんじなごかた}{Learn Chinese characters and ancient readings plus modern Japanese ones to understand modern\\ Japanese.}{TamanegiNoKame}{Chinese character know language}
\definitionpage{知字不聞}{ちじふぶん}{Knowing a word in the context of reading, because you studied it on WaniKani, but not recognizing it in conversation.}{Houndstooth}{know character not hear}
\definitionpage{知読不意}{ちどくふい}{Being able to read the kanji in a word, but not knowing the meaning.}{Houndstooth}{know read not idea}
\definitionpage{知意不読}{ちいぶどく}{Being able to understand a word written in kanji, but not knowing how it is read.}{Houndstooth}{know idea not read}
\definitionpage{撫子病気}{なでしこびょうき}{When you idealize your Japanese girlfriend to an unhealthy extent and think it makes you an important person.}{milkyrose}{smooth child sick spirit}
\definitionpage{千年禁瓜}{せんねんきんか}{Thousand year ban melon.}{RoseWagsBlue\\ and jneapan}{}
\definitionpage{雑話変更}{ざつわへんこう}{When the conversation on a particular thread starts getting sidelined}{TamanegiNoKame}{miscellaneous talk change further}
\definitionpage{過話無働}{かわむどう}{Spending too much time on the forums instead of working}{jneapan}{overdo talk no work}
\definitionpage{変色混乱}{へんいろこんらん}{When the new\\ color scheme is\\ very controversial.}{VictorLino}{usual color confuse riot}
\definitionpage{起深夜寝}{きしんやしん}{Waking up in the dead of the night to do your reviews and then going back to sleep.}{VictorLino}{rouse deep night sleep}
\definitionpage{偽了途中}{ぎりょうとちゅう}{Realizing that reaching level 60 does not mean you are done.}{rwesterhof}{falsehood finish\\ way middle}
\definitionpage{完了焼家}{かんりょうしょうか}{Member of the\\ 100\% burn club.}{rwesterhof}{perfect finish burn house}
\definitionpage{何千等字}{なんぜんとうじ}{Thousands of similar\\ symbols}{PDotAlex}{what thousand\\ similar character}
\definitionpage{心身鰐蟹}{しんしんがくかい}{Pure devotion}{RoseWagsBlue}{}
\definitionpage{六十万歳}{ろくじゅうばんざい}{Our rallying cry}{RoseWagsBlue}{six ten  ten-thousand\\ years}
\definitionpage{小食大犬 }{しょうしょくだいけん}{Small bite for a big wolf, getting Leeboed }{RoseWagsBlue}{small meal big dog}
\definitionpage{大犬小犬}{たいけんしょうけん}{Getting a “like” from Leebo}{RoseWagsBlue}{big dog small dog}
\definitionpage{良鳥無食}{りょうちょうむしょく}{Approaching Leebo}{RoseWagsBlue}{good bird no bite}
\definitionpage{一字一会 }{ いちじいちえ}{Chance encounter with a special kanji}{RoseWagsBlue}{one character one meet}
\definitionpage{底亀無亀}{ていきむき}{When you reach Durtle Heaven, and there is\\ nothing there.}{Belthazar}{bottom turtle no turtle}
\definitionpage{一駒二師}{いっくにし}{Wanikani's \emph{other}\\ programing crew, the\\ writers of scripts.  }{RoseWagsBlue}{one pony two master}


\signaturepadding

\finalpage

\end{document} 